A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
\cortext[cor1]{Corresponding author.}
\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering, University of Aberdeen, UK}

@@

It was shown that the new upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration). Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.

@@

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Principal Component Analysis (PCA) and Linear Regression \sep Singular Value Decomposition (SVD) and Higer Order Singular Value Decomposition (HOSVD) \sep Upscaling\sep Reduced Order Models (ROM), \sep Permeability field \sep Heterogeneity
\end{keyword}

>>>>

%\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
\cortext[cor1]{Corresponding author.}
\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering, University of Aberdeen, UK}

@@

It was shown that the new upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration). Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.  \red{Later}

@@

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Principal Component Analysis (PCA) \sep Linear Regression \sep Higher-Order Singular Value Decomposition (HOSVD) \sep Upscaling \sep Reduced Order Models (ROM) \sep Permeability.  
\end{keyword}
